A Lyapunov Analysis of Momentum Methods \\ in Optimization

### 2016-11-08 Draft14.tex
Update Draft14.tex

Since the vector field explicitly depends on time, \eqref{Eq:MirrorTime} is no longer a gradient flow. Nevertheless, a we can generate a Lyapunov function from the general time-dilated dynamic. 

@@

Integrating gives a Lyapunov function for the mirror descent dynamic~\eqref{Eq:MirrorFlow}.

%
  %%%%%%%%%%%%%%%%%
    \section{Momentum Algorithms}
        \label{App:Momentum}
\subsection{Proof of Theorem~\ref{Thm:Quasi}}
\label{App:ProofQuasi}
We use the Lyapunov function 
\begin{equation*}
E_k = A_k (f(x_k) - f(x^\ast)) + D_h(x^\ast, z_k)
\end{equation*}
to obtain a convergence guarantee for the quasi-monotone subgradient method~\eqref{Eq:QuasiSub}.
Denoting $D^\ast_{k+1, k} = D_h(x^\ast,z_{k+1})- D_h(x^\ast,z_{k})$, observe that
%\label{App:ProofQuasi}
%\begin{small}
\begin{subequations}
\begin{align}
D^\ast_{k+1, k}  &= -D_h(z_{k+1}, z_k) +  \langle \nabla h(z_{k+1}) - \nabla h(z_k), z_{k+1} - x^\ast\rangle \label{Eq:Mirror}\\
&\overset{\eqref{Eq:XSeqQuasi}}{\leq} -\frac{1}{2}\|z_k - z_{k+1}\|^2 -(A_{k+1} -A_{k}) \langle \nabla f(x_{k+1}), z_{k+1} - x^\ast\rangle \label{Eq:StrongConvAssump1} \\
&= -\frac{1}{2}\|z_k - z_{k+1}\|^2 - (A_{k+1} -A_{k}) \langle \nabla f(x_{k+1}), z_{k+1} - z_k\rangle -(A_{k+1} -A_{k}) \langle \nabla f(x_{k+1}), z_k - x^\ast\rangle \notag\\
&\leq\frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2 - (A_{k+1} -A_{k}) \langle \nabla f(x_{k+1}), z_k - x^\ast\rangle \label{Eq:HoldBound1}\\
& \overset{\eqref{Eq:ZSeqQuasi}}{=}\frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2 - (A_{k+1} - A_k) \left\langle \nabla f(x_{k+1}), \frac{A_{k+1}}{(A_{k+1} -A_{k})}(x_{k+1} - x_k) + x_k - x^\ast\right\rangle \notag \\
& =\frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2- A_{k+1} \left\langle \nabla f(x_{k+1}), x_{k+1} - x_k\right\rangle - (A_{k+1} -A_{k})\langle \nabla f(x_{k+1}), x_{k+1} - x^\ast\rangle \notag\\
&\quad + (A_{k+1} -A_{k})\langle \nabla f(x_{k+1}), x_{k+1} - x_k \rangle \notag\\
& = \frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2- A_{k} \langle \nabla f(x_{k+1}), x_{k+1} - x_k\rangle  - (A_{k+1} -A_{k})\langle \nabla f(x_{k+1}), x_{k+1} - x^\ast\rangle. \notag\\
&\leq A_k(f(x_{k}) - f(x_{k+1})) - (A_{k+1} -A_{k})(f(x_{k+1}) - f(x^\ast)) + \frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2 \notag\\
& = A_k (f(x_k) - f(x^\ast)) - A_{k+1}(f(x_{k+1}) - f(x^\ast)) + \frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2 \notag
\end{align}
\end{subequations}
%\end{small}
where \eqref{Eq:StrongConvAssump1} follows from the strong convexity assumption on $h$, and \eqref{Eq:HoldBound1} uses the Fenchel-Young inequality. Thus, we obtain the following bound,
\begin{subequations}
\begin{align*}
E_{k+1} - E_k &\leq  \frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2. 
\end{align*}
\end{subequations}
%Choosing $\sum_{i=0}^k (A_{i+1} -A_{i})^2  < \infty$ gives the convergence rate
%%\begin{align*}
%%E_{k} \leq E_0 + \frac{1}{2}\sum_{i=0}^{k} (A_{i+1} -A_{i})^2 \|\nabla f(x_{i})\|_\ast^2,
%%\end{align*}
%%which we can write as
%\begin{align}\label{Eq:ConvQuasi}
%f(x_k) - f(x^\ast) \leq \frac{D_h(x^\ast , x_0) +A_0 (f(x_0) - f(x^\ast)) + \frac{1}{2}\sum_{i=0}^{k} (A_{i+1} -A_{i})^2\|\nabla f(x_{i})\|_\ast^2}{A_k}.
%\end{align}

%%%%%%%%%%%%%%%%
\subsection{Proof of General Quasi-Monotone Method}
\label{App:ProofQuasiGen}
In \ref{App:ProofQuasi} we have set  the dual averaging term $\gamma_k \equiv 1$  for simplicity.
%\noindent The proof of Theorem~\ref{Thm:Quasi} can be found in Appendix.
%Notice, we have set the dual averaging term $\gamma_k \equiv 1$. This is for simplicity of the presentation. 
In its more general form, we add an increasing sequence $\{\gamma_k\}_{k=1}^\infty$ to the algorithm, and~\eqref{Eq:XSeqQuasi1} can be written as, 
\begin{equation*}
z_k = \arg \min_{z\in \X} \left\{ \sum_{i=1}^k \alpha_i \langle \nabla f(x_i), z\rangle + \gamma_kD_h(z, z_0)\right\} \label{Eq:XSeqQuasi2},
\end{equation*}
which satisfies the optimality condition,
\begin{align}\label{Eq:DualAvgX}
\gamma_{k+1} \nabla h(x_{k+1})  - \gamma_k \nabla h(x_k)  =-(A_{k+1} - A_{k}) \nabla f(x_{k+1}).
\end{align}
For this method, the notion of a ``prox-center'' is essential. We provide an analysis of  this algorithm using the discrete Lyapunov function 
\begin{equation}\label{Eq:Lyap3}
E_k = A_k(f(x_k) - f(x^\ast)) + \gamma_k (D_h(x^\ast, z_k) -D_h(x^\ast, x_0)).
\end{equation}
First however, we analyze the dynamics and show how to obtain the discrete Lyapunov function~\eqref{Eq:Lyap3} for the dual-averaged algorithm.

 \paragraph{The dynamics} We analyze the momentum dynamics~\eqref{Eq:ELBreg} with an additional increasing weighting term ($\dot \gamma_t \geq 0$), which we require to be positive $\gamma_t\geq 0$, $\forall t\in \R$:
 \begin{subequations}\label{Eq:DualAvgDyn}
\begin{align}
\frac{d}{dt}\Big(\gamma_t \nabla h(Z_t)\Big) &= -\dot \beta_t e^{\beta_t}\nabla f(X_t)\\
Z_t &= X_t + \frac{1}{\beta_t} \dot X_t.
\end{align}
\end{subequations}
With this additional weighting term we obtain the following bound, 
\begin{subequations}\label{Eq:Last}
  \begin{align}
 \frac{d}{dt} \Big( \gamma_t D_h(x^\ast,Z_t) \Big) \, dt
&=\dot \gamma_t [h(x^\ast) - h(Z_t)] - \dot \gamma_t \langle\nabla h(Z_t), x - Z_t \rangle-\gamma_t\left \langle \frac{d}{dt} \nabla h(Z_t), x - Z_t\right \rangle \notag\\
&= \dot \gamma_t [h(x^\ast) - h(Z_t)] - \left \langle \frac{d}{dt} \Big(\gamma_t  \nabla h(Z_t)\Big), x^\ast - Z_t \right\rangle \notag\\
&  \overset{\eqref{Eq:DualAvgDyn}}{=}  \gamma_t [h(x^\ast) - h(Z_t)]  +  \dot \beta_t e^{\beta_t} \left\langle \nabla f(X_t), x^\ast - X_t - \frac{1}{\dot \beta_t} \dot X_t\right\rangle \notag\\
& \overset{\eqref{Eq:LyapAnal}}{\leq} \dot \gamma_t [h(x^\ast) - h(Z_t)]   - \frac{d}{dt}\left( e^{\beta_t}\left(f(X_t) - f(x^\ast)\right)\right) 
%& \leq  \int_0^t \dot \gamma_s D_h(x^\ast, Z_0)  -\int_0^t \frac{d}{ds}\left\{ e^{\beta_s}\left(f(X_s) - f(x^\ast)\right)\right\} ds,
\end{align}
\end{subequations}
\paragraph{Prox-Center}  We now require $\X$ to be a compact set,  and  define $X_0$ to be the ``prox-center,'' of $\X$:
\begin{align*}
X_0 = \arg\min_{x \in \X} \,h(x).
\end{align*}
Without loss of generality, we choose $h(X_0) = 0$, so that $h(x) =D_h(x,X_0) \geq 0, \, \forall x \in \X$.
Using this definition and rearranging~\eqref{Eq:Last}, we obtain the following bound:
% \begin{align*}
%\int_0^t \frac{d}{ds} \left\{ \gamma_s D_h(x^\ast,Z_s) \right\} \, ds \leq  \int_0^t \frac{d}{ds}\left\{\gamma_s D_h(x^\ast, X_0)\right\}  -\int_0^t \frac{d}{ds}\left\{ e^{\beta_s}\left(f(X_s) - f(x^\ast)\right)\right\} ds
%\end{align*}
%
\begin{align*}
 \frac{d}{dt}\left( e^{\beta_t}\left(f(X_t) - f(x^\ast)\right)\right) \,\leq  \frac{d}{dt} \Big( \gamma_t D_h(x^\ast, Z_0) -\gamma_t D_h(x^\ast,Z_t) \Big) ,
\end{align*}
from which we can conclude that the following function, 
\begin{equation}
\E_t = e^{\beta_t}( f(X_t) - f(x^\ast)) + \gamma_t (D_h(x^\ast, Z_t) - D_h(x^\ast, Z_0)),
\end{equation}
is a Lyapunov function. We can also conclude the following convergence rate guarantee, 
\begin{equation}\label{Eq:DualAvgBound}
f(X_t) - f(X_0) \leq \frac{\gamma_t D_h(x^\ast,Z_0)}{e^{\beta_t}}.
\end{equation}

\paragraph{The Algorithm} 

@@

&\quad+ (\gamma_{k+1} - \gamma_{k})D_h(x^\ast, x_0).\notag

@@

This matches the bound Nesterov obtained in \cite{Nesterov15}. Note, that a very similar analysis can be presented for Nesterov's dual averaging algorithm~\cite{Nesterov09}.

%%%%%%%%%%%%%%%%%%%%FRANK WOLFE PROOF %%%%%%%%%%%%%
\subsection{Proof of Discretizations}
\label{App:OtherDiscret}
\subsubsection{Proof of Method 1} We analyze the algorithm~\eqref{Eq:QuasiSub2} using the Lyapunov function~\eqref{Eq:DiscLyapFunc1}. 
\begin{subequations}
\begin{align}
E_{k+1} - E_k %&= A_{k+1}(f(x_{k+1}) -f(x^\ast)) - A_k(f(x_k) - f(x^\ast)) + D_h(x^\ast, z_{k+1}) - D_h(x^\ast, z_k) \notag\\
&= A_{k+1}(f(x_{k+1}) -f(x_k)) + \alpha_k(f(x_k) - f(x^\ast)) - \langle \nabla h(z_{k+1}) - \nabla h(z_k), x^\ast - z_{k+1} \rangle\notag\\
&\quad- D_h(z_{k+1}, z_k) \notag\\
 &= A_{k+1}(f(x_{k+1}) -f(x_k)) + \alpha_k(f(x_k) - f(x^\ast)) + (A_{k+1} - A_k)\langle \nabla f(x_k), x^\ast - x_{k+1}\rangle \notag\\
 &\quad -A_{k} \langle \nabla f(x_k), x_{k+1} - x_k\rangle - D_h(z_{k+1}, z_k) \label{Eq:Stuff}\\
 &= A_{k+1}(f(x_{k+1}) -f(x_k)) + \alpha_k(f(x_k) - f(x^\ast)) + (A_{k+1} - A_k)\langle \nabla f(x_k), x^\ast - x_{k}\rangle \notag\\
 &\quad  + (A_{k+1} - A_k)\langle \nabla f(x_k), x_{k}- x_{k+1}\rangle -A_{k} \langle \nabla f(x_k), x_{k+1} - x_k\rangle - D_h(z_{k+1}, z_k)\notag\\
  &= A_{k+1}(f(x_{k+1}) -f(x_k) - \langle \nabla f(x_k), x_{k+1} - x_k\rangle) + \alpha_k(f(x_k) - f(x^\ast)+\langle \nabla f(x_k), x^\ast - x_{k}\rangle)  \notag \\ &\quad- D_h(z_{k+1}, z_k) \notag\\
 & \leq A_{k+1} \frac{L}{2}\| x_{k+1} - x_{k}\|^2 \notag\\
% & =\frac{1}{2} \frac{A_{k+1}\alpha_k^2}{A_{k}^2} \|x_{k+1} - z_{k+1}\|^ 2\\
& \overset{\eqref{Eq:XSeqOther1}}{\leq}  \frac{L}{2} \frac{A_{k+1}\alpha_k^2}{A_{k}^2}diam(\X)^2
\end{align}
\end{subequations}
%\end{small}
where in~\eqref{Eq:Stuff} we used~\eqref{Eq:XSeqOther1} and~\eqref{Eq:ZSeqOther1}. Therefore, we obtain the following upper bound, 
\begin{align*}
f(x_k) - f(x^\ast) \leq \frac{D_h(x^\ast, x_0) + A_0(f(x_0)- f(x^\ast)) +  \frac{L}{2}\sum_{i=1}^k \frac{A_{i+1}(A_{i+1} - A_{i})^2}{A_{i}^2}diam(\X)^2 }{A_k}.
\end{align*}
Choosing $A_k = \frac{k(k+1)}{2}$ gives a $O(1/k)$ convergence rate.

@@

%%%%%%%%%%%%%%%%%%%%FRANK WOLFE PROOF %%%%%%%%%%%%%
\subsection{Proof of Conditional Gradient Method}
\label{App:CondMethod}
We use the Lyapunov function \eqref{Eq:FrankWolfeLyap} to analyze conditional gradient method~\eqref{eq:Frank-WolfeAlgo}
\label{App:ProofAccGrad}
\begin{subequations}
\begin{align*}
E_{k+1} - E_k &= A_{k+1}(f(x_{k+1}) -f(x^\ast)) - A_k(f(x_k) - f(x^\ast)) \notag\\
& = A_{k+1}(f(x_{k+1}) -f(x_k)) - \alpha_{k+1}(f(x_k) - f(x^\ast))\notag\\
&  \leq A_{k+1}(\langle \nabla f(x_k), x_{k+1} - x_k \rangle + \frac{L}{2}\|x_{k+1} - x_k\|^2) - \alpha_{k+1} (f(x_k) - f(x^\ast)) \\
& = A_{k+1}(\tau_k\langle \nabla f(x_k), z_k- x_k \rangle + \frac{L\tau_k^2}{2}\|z_k - x_k\|^2) - \alpha_{k+1} (f(x_k) - f(x^\ast)) \\
&= \alpha_{k+1} \langle \nabla f(x_k), z_k- x_k \rangle + \frac{L}{2}\frac{\alpha_{k+1}^2}{A_{k+1}}\|z_k - x_k\|^2 - \alpha_{k} (f(x_k) - f(x^\ast))\\
& \leq \alpha_{k+1} ( f(x^\ast) - f(x_k) + \langle \nabla f(x_k), x^\ast -  x_k \rangle) + \frac{L}{2}\frac{\alpha_{k+1}^2}{A_{k+1}}\|z_k - x_k\|^2  \\
& \leq \frac{L}{2}\frac{\alpha_{k+1}^2}{A_{k+1}}diam(\X)^2.
\end{align*}
\end{subequations}
Therefore, 
\begin{align*}
E_k \leq E_0 + \frac{L}{2} diam(\X)^2\sum_{i=0}^k \frac{\alpha_{i}^2}{A_{k}}.
\end{align*}
Choosing $A_{k+1} = \frac{k(k+1)}{2}$ gives the coupling term $\tau_k = \frac{2}{k+2}$ and $O(1/k)$ convergence rate. This recovers the bounds shown by Nesterov~\cite{NesterovCond15}.

>>>>

Since the vector field explicitly depends on time, \eqref{Eq:MirrorTime} is no longer a gradient flow. Nevertheless, a we can generate a Lyapunov function from the general time-dilated dynamics. 

@@

Integrating gives a Lyapunov function for the mirror descent dynamics~\eqref{Eq:MirrorFlow}.

%
  %%%%%%%%%%%%%%%%%
    \section{Momentum Algorithms}
        \label{App:Momentum}
\subsection{Proof of Theorem~\ref{Thm:Quasi}}
\label{App:ProofQuasi}
We use the Lyapunov function 
\begin{equation*}
E_k = A_k (f(x_k) - f(x^\ast)) + D_h(x^\ast, z_k)
\end{equation*}
to obtain a convergence guarantee for the quasi-monotone subgradient method~\eqref{Eq:QuasiSub}.
Denoting $D^\ast_{k+1, k} = D_h(x^\ast,z_{k+1})- D_h(x^\ast,z_{k})$, observe that
%\label{App:ProofQuasi}
%\begin{small}
\begin{subequations}
\begin{align}
D^\ast_{k+1, k}  &= -D_h(z_{k+1}, z_k) +  \langle \nabla h(z_{k+1}) - \nabla h(z_k), z_{k+1} - x^\ast\rangle \label{Eq:Mirror}\\
&\overset{\eqref{Eq:XSeqQuasi}}{\leq} -\frac{1}{2}\|z_k - z_{k+1}\|^2 -(A_{k+1} -A_{k}) \langle \nabla f(x_{k+1}), z_{k+1} - x^\ast\rangle \label{Eq:StrongConvAssump1} \\
&= -\frac{1}{2}\|z_k - z_{k+1}\|^2 - (A_{k+1} -A_{k}) \langle \nabla f(x_{k+1}), z_{k+1} - z_k\rangle -(A_{k+1} -A_{k}) \langle \nabla f(x_{k+1}), z_k - x^\ast\rangle \notag\\
&\leq\frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2 - (A_{k+1} -A_{k}) \langle \nabla f(x_{k+1}), z_k - x^\ast\rangle \label{Eq:HoldBound1}\\
& \overset{\eqref{Eq:ZSeqQuasi}}{=}\frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2 - (A_{k+1} - A_k) \left\langle \nabla f(x_{k+1}), \frac{A_{k+1}}{(A_{k+1} -A_{k})}(x_{k+1} - x_k) + x_k - x^\ast\right\rangle \notag \\
& =\frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2- A_{k+1} \left\langle \nabla f(x_{k+1}), x_{k+1} - x_k\right\rangle - (A_{k+1} -A_{k})\langle \nabla f(x_{k+1}), x_{k+1} - x^\ast\rangle \notag\\
&\quad + (A_{k+1} -A_{k})\langle \nabla f(x_{k+1}), x_{k+1} - x_k \rangle \notag\\
& = \frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2- A_{k} \langle \nabla f(x_{k+1}), x_{k+1} - x_k\rangle  - (A_{k+1} -A_{k})\langle \nabla f(x_{k+1}), x_{k+1} - x^\ast\rangle. \notag\\
&\leq A_k(f(x_{k}) - f(x_{k+1})) - (A_{k+1} -A_{k})(f(x_{k+1}) - f(x^\ast)) + \frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2 \notag\\
& = A_k (f(x_k) - f(x^\ast)) - A_{k+1}(f(x_{k+1}) - f(x^\ast)) + \frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2, \notag
\end{align}
\end{subequations}
%\end{small}
where \eqref{Eq:StrongConvAssump1} follows from the strong convexity assumption on $h$, and \eqref{Eq:HoldBound1} uses the Fenchel-Young inequality. Thus, we obtain the following bound,
\begin{subequations}
\begin{align*}
E_{k+1} - E_k &\leq  \frac{(A_{k+1} -A_{k})^2}{2} \|\nabla f(x_{k+1})\|_\ast^2. 
\end{align*}
\end{subequations}
%Choosing $\sum_{i=0}^k (A_{i+1} -A_{i})^2  < \infty$ gives the convergence rate
%%\begin{align*}
%%E_{k} \leq E_0 + \frac{1}{2}\sum_{i=0}^{k} (A_{i+1} -A_{i})^2 \|\nabla f(x_{i})\|_\ast^2,
%%\end{align*}
%%which we can write as
%\begin{align}\label{Eq:ConvQuasi}
%f(x_k) - f(x^\ast) \leq \frac{D_h(x^\ast , x_0) +A_0 (f(x_0) - f(x^\ast)) + \frac{1}{2}\sum_{i=0}^{k} (A_{i+1} -A_{i})^2\|\nabla f(x_{i})\|_\ast^2}{A_k}.
%\end{align}

%%%%%%%%%%%%%%%%
\subsection{Proof of General Quasi-Monotone Method}
\label{App:ProofQuasiGen}
In \ref{App:ProofQuasi} we have set  the dual averaging term $\gamma_k \equiv 1$  for simplicity.
%\noindent The proof of Theorem~\ref{Thm:Quasi} can be found in Appendix.
%Notice, we have set the dual averaging term $\gamma_k \equiv 1$. This is for simplicity of the presentation. 
In its more general form, we add an increasing sequence $\{\gamma_k\}_{k=1}^\infty$ to the algorithm, and~\eqref{Eq:XSeqQuasi1} can be written as, 
\begin{equation*}
z_k = \arg \min_{z\in \X} \left\{ \sum_{i=1}^k \alpha_i \langle \nabla f(x_i), z\rangle + \gamma_kD_h(z, z_0)\right\} \label{Eq:XSeqQuasi2},
\end{equation*}
which satisfies the optimality condition,
\begin{align}\label{Eq:DualAvgX}
\gamma_{k+1} \nabla h(x_{k+1})  - \gamma_k \nabla h(x_k)  =-(A_{k+1} - A_{k}) \nabla f(x_{k+1}).
\end{align}
For this method, the notion of a ``prox-center'' is essential. We provide an analysis of  this algorithm using the discrete Lyapunov function 
\begin{equation}\label{Eq:Lyap3}
E_k = A_k(f(x_k) - f(x^\ast)) + \gamma_k (D_h(x^\ast, z_k) -D_h(x^\ast, x_0)).
\end{equation}
First, however, we analyze the dynamics and show how to obtain the discrete Lyapunov function~\eqref{Eq:Lyap3} for the dual-averaged algorithm.

 \paragraph{The dynamics} We analyze the momentum dynamics~\eqref{Eq:ELBreg} with an additional increasing weighting term ($\dot \gamma_t \geq 0$), which we require to be positive, $\gamma_t\geq 0$, $\forall t\in \R$:
 \begin{subequations}\label{Eq:DualAvgDyn}
\begin{align}
\frac{d}{dt}\Big(\gamma_t \nabla h(Z_t)\Big) &= -\dot \beta_t e^{\beta_t}\nabla f(X_t)\\
Z_t &= X_t + \frac{1}{\beta_t} \dot X_t.
\end{align}
\end{subequations}
With this additional weighting term we obtain the following bound, 
\begin{subequations}\label{Eq:Last}
  \begin{align}
 \frac{d}{dt} \Big( \gamma_t D_h(x^\ast,Z_t) \Big) \, dt
&=\dot \gamma_t [h(x^\ast) - h(Z_t)] - \dot \gamma_t \langle\nabla h(Z_t), x - Z_t \rangle-\gamma_t\left \langle \frac{d}{dt} \nabla h(Z_t), x - Z_t\right \rangle \notag\\
&= \dot \gamma_t [h(x^\ast) - h(Z_t)] - \left \langle \frac{d}{dt} \Big(\gamma_t  \nabla h(Z_t)\Big), x^\ast - Z_t \right\rangle \notag\\
&  \overset{\eqref{Eq:DualAvgDyn}}{=}  \gamma_t [h(x^\ast) - h(Z_t)]  +  \dot \beta_t e^{\beta_t} \left\langle \nabla f(X_t), x^\ast - X_t - \frac{1}{\dot \beta_t} \dot X_t\right\rangle \notag\\
& \overset{\eqref{Eq:LyapAnal}}{\leq} \dot \gamma_t [h(x^\ast) - h(Z_t)]   - \frac{d}{dt}\left( e^{\beta_t}\left(f(X_t) - f(x^\ast)\right)\right).
%& \leq  \int_0^t \dot \gamma_s D_h(x^\ast, Z_0)  -\int_0^t \frac{d}{ds}\left\{ e^{\beta_s}\left(f(X_s) - f(x^\ast)\right)\right\} ds,
\end{align}
\end{subequations}
\paragraph{Prox-center}  We now require $\X$ to be a compact set,  and  define $X_0$ to be the ``prox-center'' of $\X$:
\begin{align*}
X_0 = \arg\min_{x \in \X} \,h(x).
\end{align*}
Without loss of generality, we choose $h(X_0) = 0$, so that $h(x) =D_h(x,X_0) \geq 0, \, \forall x \in \X$.
Using this definition and rearranging~\eqref{Eq:Last}, we obtain the following bound:
% \begin{align*}
%\int_0^t \frac{d}{ds} \left\{ \gamma_s D_h(x^\ast,Z_s) \right\} \, ds \leq  \int_0^t \frac{d}{ds}\left\{\gamma_s D_h(x^\ast, X_0)\right\}  -\int_0^t \frac{d}{ds}\left\{ e^{\beta_s}\left(f(X_s) - f(x^\ast)\right)\right\} ds
%\end{align*}
%
\begin{align*}
 \frac{d}{dt}\left( e^{\beta_t}\left(f(X_t) - f(x^\ast)\right)\right) \,\leq  \frac{d}{dt} \Big( \gamma_t D_h(x^\ast, Z_0) -\gamma_t D_h(x^\ast,Z_t) \Big) ,
\end{align*}
from which we can conclude that the following function, 
\begin{equation}
\E_t = e^{\beta_t}( f(X_t) - f(x^\ast)) + \gamma_t (D_h(x^\ast, Z_t) - D_h(x^\ast, Z_0)),
\end{equation}
is a Lyapunov function. We also obtain the following convergence rate guarantee, 
\begin{equation}\label{Eq:DualAvgBound}
f(X_t) - f(X_0) \leq \frac{\gamma_t D_h(x^\ast,Z_0)}{e^{\beta_t}}.
\end{equation}

\paragraph{The algorithm} 

@@

&\quad+ (\gamma_{k+1} - \gamma_{k})D_h(x^\ast, x_0),\notag

@@

This matches the bound Nesterov obtained in \cite{Nesterov15}. Note that a very similar analysis can be presented for Nesterov's dual averaging algorithm~\cite{Nesterov09}.

%%%%%%%%%%%%%%%%%%%%FRANK WOLFE PROOF %%%%%%%%%%%%%
\subsection{Proof of Discretizations}
\label{App:OtherDiscret}
\subsubsection{Proof of Method 1} We analyze the algorithm~\eqref{Eq:QuasiSub2} using the Lyapunov function~\eqref{Eq:DiscLyapFunc1}: 
\begin{subequations}
\begin{align}
E_{k+1} - E_k %&= A_{k+1}(f(x_{k+1}) -f(x^\ast)) - A_k(f(x_k) - f(x^\ast)) + D_h(x^\ast, z_{k+1}) - D_h(x^\ast, z_k) \notag\\
&= A_{k+1}(f(x_{k+1}) -f(x_k)) + \alpha_k(f(x_k) - f(x^\ast)) - \langle \nabla h(z_{k+1}) - \nabla h(z_k), x^\ast - z_{k+1} \rangle\notag\\
&\quad- D_h(z_{k+1}, z_k) \notag\\
 &= A_{k+1}(f(x_{k+1}) -f(x_k)) + \alpha_k(f(x_k) - f(x^\ast)) + (A_{k+1} - A_k)\langle \nabla f(x_k), x^\ast - x_{k+1}\rangle \notag\\
 &\quad -A_{k} \langle \nabla f(x_k), x_{k+1} - x_k\rangle - D_h(z_{k+1}, z_k) \label{Eq:Stuff}\\
 &= A_{k+1}(f(x_{k+1}) -f(x_k)) + \alpha_k(f(x_k) - f(x^\ast)) + (A_{k+1} - A_k)\langle \nabla f(x_k), x^\ast - x_{k}\rangle \notag\\
 &\quad  + (A_{k+1} - A_k)\langle \nabla f(x_k), x_{k}- x_{k+1}\rangle -A_{k} \langle \nabla f(x_k), x_{k+1} - x_k\rangle - D_h(z_{k+1}, z_k)\notag\\
  &= A_{k+1}(f(x_{k+1}) -f(x_k) - \langle \nabla f(x_k), x_{k+1} - x_k\rangle) + \alpha_k(f(x_k) - f(x^\ast)+\langle \nabla f(x_k), x^\ast - x_{k}\rangle)  \notag \\ &\quad- D_h(z_{k+1}, z_k) \notag\\
 & \leq A_{k+1} \frac{L}{2}\| x_{k+1} - x_{k}\|^2 \notag\\
% & =\frac{1}{2} \frac{A_{k+1}\alpha_k^2}{A_{k}^2} \|x_{k+1} - z_{k+1}\|^ 2\\
& \overset{\eqref{Eq:XSeqOther1}}{\leq}  \frac{L}{2} \frac{A_{k+1}\alpha_k^2}{A_{k}^2}diam(\X)^2,
\end{align}
\end{subequations}
%\end{small}
where in~\eqref{Eq:Stuff} we used~\eqref{Eq:XSeqOther1} and~\eqref{Eq:ZSeqOther1}. Therefore, we obtain the following upper bound, 
\begin{align*}
f(x_k) - f(x^\ast) \leq \frac{D_h(x^\ast, x_0) + A_0(f(x_0)- f(x^\ast)) +  \frac{L}{2}\sum_{i=1}^k \frac{A_{i+1}(A_{i+1} - A_{i})^2}{A_{i}^2}diam(\X)^2 }{A_k}.
\end{align*}
Choosing $A_k = \frac{k(k+1)}{2}$ gives a $O(1/k)$ convergence rate.

@@

%%%%%%%%%%%%%%%%%%%%FRANK WOLFE PROOF %%%%%%%%%%%%%
\subsection{Proof of Conditional Gradient Method}
\label{App:CondMethod}
We use the Lyapunov function \eqref{Eq:FrankWolfeLyap} to analyze conditional gradient method~\eqref{eq:Frank-WolfeAlgo}:
\label{App:ProofAccGrad}
\begin{subequations}
\begin{align*}
E_{k+1} - E_k &= A_{k+1}(f(x_{k+1}) -f(x^\ast)) - A_k(f(x_k) - f(x^\ast)) \notag\\
& = A_{k+1}(f(x_{k+1}) -f(x_k)) - \alpha_{k+1}(f(x_k) - f(x^\ast))\notag\\
&  \leq A_{k+1}(\langle \nabla f(x_k), x_{k+1} - x_k \rangle + \frac{L}{2}\|x_{k+1} - x_k\|^2) - \alpha_{k+1} (f(x_k) - f(x^\ast)) \\
& = A_{k+1}(\tau_k\langle \nabla f(x_k), z_k- x_k \rangle + \frac{L\tau_k^2}{2}\|z_k - x_k\|^2) - \alpha_{k+1} (f(x_k) - f(x^\ast)) \\
&= \alpha_{k+1} \langle \nabla f(x_k), z_k- x_k \rangle + \frac{L}{2}\frac{\alpha_{k+1}^2}{A_{k+1}}\|z_k - x_k\|^2 - \alpha_{k} (f(x_k) - f(x^\ast))\\
& \leq \alpha_{k+1} ( f(x^\ast) - f(x_k) + \langle \nabla f(x_k), x^\ast -  x_k \rangle) + \frac{L}{2}\frac{\alpha_{k+1}^2}{A_{k+1}}\|z_k - x_k\|^2  \\
& \leq \frac{L}{2}\frac{\alpha_{k+1}^2}{A_{k+1}}diam(\X)^2.
\end{align*}
\end{subequations}
Therefore, 
\begin{align*}
E_k \leq E_0 + \frac{L}{2} diam(\X)^2\sum_{i=0}^k \frac{\alpha_{i}^2}{A_{k}}.
\end{align*}
Choosing $A_{k+1} = \frac{k(k+1)}{2}$ gives the coupling term $\tau_k = \frac{2}{k+2}$ and $O(1/k)$ convergence rate. This recovers the bounds shown by Nesterov~\cite{NesterovCond15}.
